### 2015-03-11 article/article.tex
commit
presentation changes

Table~\ref{tab:top10pheno} shows the strains and gene names associated with the most significant MPD phenotypes. 

@@

\begin{tabulary}{\linewidth}{ LLLLL }

@@

	NOD/ShiLtJ  & Ppard (peroxisome proliferator activator receptor delta) & 

>>>>

Table~\ref{tab:top10pheno} shows the strains and gene names associated with the highest ranking MPD phenotypes relative to their Z-scores. 

@@

\begin{tabulary}{\linewidth}{ LLLL }

@@

	NOD/\\ShiLtJ & Ppard (peroxisome proliferator activator receptor delta) & 
